Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-03 paper.tex
done site energies

\subsection{Distributions of site energies}

@@

%\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
%\caption{\label{tab:W2_E}%
%The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
%}
%\begin{ruledtabular}
%  \begin{tabular}{c c c c c c}
%  $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
%    \hline
%  $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
%  $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
%  $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
%  $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
%    \end{tabular}
%\end{ruledtabular}
%\end{table*}
%

\begin{figure*}
  \centering
  \includegraphics[width=0.80\textwidth]{figs/scatterE_qmmm.pdf}
  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
  \label{fig:E_qmmm_MADN}
\end{figure*}

Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference for which the calculated molecule energy has a range from -1.17 to -0.60 \unit[]{eV}y.
The range of molecule energy for the other five HFX are: 
from -1.11 to -0.59 \unit[]{eV} for $\alpha=0$, 
from -1.07 to -0.63 \unit[]{eV} for $\alpha=0.05$, 
from -1.13 to -0.61 \unit[]{eV} for $\alpha=0.10$
from -1.16 to -0.60 \unit[]{eV} for $\alpha=0.15$, 
and from -1.12 to -0.63 \unit[]{eV} for $\alpha=0.20$.
The bright-yellow color in all plots of Fig. \ref{fig:E_qmmm_MADN} indicates that most data points are clustering near the diagonal line, so the molecular energies calculated by different HFX are very close.

%To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
%Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
%The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
%\begin{eqnarray}
%    && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
%    && \frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |
%\end{eqnarray}
%where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$. The 1-Wasserstein distance between two empirical distributions for each plot in Fig. \ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}. $W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that the molecular energy distributions are very similar.

To further estimate the energy variation due to HFX, one can look at the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ for all molecule index $i=1,2,\cdots,N$. 
This quantity provides information of the amount of the largest variation one can expect in $E_i(\alpha)$. Index the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ to be $i'$. 
If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further change (such as lowering) in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics and significantly affects the mobility.

Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy and the magnitude of the energy disorder, which is around 0.08 as shown in Fig. \ref{fig:autogen_MADN}. 
The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system. So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.

\begin{table}[tbp]
\caption{\label{tab:maxEi}%
In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules. Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$. The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$. All the energies are in unit $\unit[]{eV}$.
}
\begin{ruledtabular}
  \begin{tabular}{c c c c}
  $\alpha'$ & $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$  & $E_{i'}(\alpha=0.25)$ & $E_{i'}(\alpha')$ \\
    \hline
  0 & 0.13 &  -1.07 & -0.94 \\
  0.05 & 0.12 & -0.82 & -0.94 \\
  0.10 & 0.13 & -1.07 & -0.94 \\
  0.15 & 0.15 & -0.84 & -0.69 \\
  0.20 & 0.12 & -0.70 & -0.82 \\
    \end{tabular}
\end{ruledtabular}
\end{table}

Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistently close to the ones calculated from $\alpha=0.25$, since all the points comparing $E^\text{el}_i(\alpha')$ and $E^\text{el}_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
The range of $E^\text{el}$ calculated by different $\alpha$ is as follows:
from  -0.55 to 0.078 eV for $\alpha=0$, 
from  -0.52 to 0.047 eV for $\alpha=0.05$, 
from  -0.57 to 0.086 eV for $\alpha=0.10$, 
from  -0.59 to 0.14 eV for $\alpha=0.15$, 
from  -0.57 to 0.10 eV for $\alpha=0.20$, 
and from -0.63 to 0.10 eV for $\alpha=0.25$.

The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at the third row at Table \ref{tab:W2_E}. 
The maximum of $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ 0.012. The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table \ref{tab:W2_E}, with a maximum of 0.006. So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.

The standard deviations of the electrostatic energy are 0.099, 0.094, 0.099, 0.11, 0.10, \unit[0.10]{eV}, and the standard deviations of the polarization energies are 0.044, 0.043, 0.043, 0.047, 0.045, \unit[0.045]{eV}. So the disorder in electrostatic energies is consistently larger than that in molecule energies, and the palorization effect reduces the electrostatic energy disorder. 
Each individual molecule has similar polarization energies under different HFX calculation, in spite of $P_\text{iso}$ is linearly dependent on HFX.

\subsection{Distributions of electronic couplings}

>>>>

\subsection{Site energies}

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
  \caption{\bjoern{TODO: }{rewrite caption}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
  \label{fig:E_qmmm_MADN}
\end{figure*}

\begin{table}[tbp]
  \caption{\bjoern{TODO: }{rewrite caption}In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules. Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$. The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$. All the energies are in unit $\unit[]{eV}$.}
  \begin{ruledtabular}
    \begin{tabular}{c c c c c c c}
    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\%  & $E_{i_\text{max}}$ \\
    \hline
    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ %&  -0.94 \\
    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ %&  -0.69 \\
    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ %&  -0.82 \\
    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ %&   ---\\
    \end{tabular}
  \end{ruledtabular}
  \label{tab:maxEi}
\end{table}

Figure~\ref{fig:E_qmmm_MADN}(a)-(e) presents scatter plots comparing the distributions of the calculated site energies of MADN molecules for different \ahfx values, using $\ahfx = \unit[0.25]{}$ (PBE0 functional) as a reference in all cases. Visually, the distributions look very similar as most data points cluster near the diagonal line. In Table~\ref{tab:maxEi}, we report the minimum ($E_\text{min}$) and maximum ($E_\text{max}$) values of the energies and the standard deviation $\sigma$ of the individual distributions, which are also shown in Fig.~\ref{fig:E_qmmm_MADN}(f). All noted variations in these quantities appear small. The data in Figures~\ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} in the Appendix show that the observations on the total site energies also hold for the individual contributions of electrostatic and polarization energies. This is also reflected by the small variations in the respective standard deviations $\sigma_\text{el}$ and $\sigma_\text{polar}$ listed in Tab.~\ref{tab:maxEi}.

Interestingly, we find the biggest variation of \unit[0.1]{eV} in the values for $E_\text{min}$. This minimal energy (or rather all the energies in the low-energy region of the distributions) can have a very significant influence on the charge transport properties, depending on how much the site energy differences are influenced in the charge transport network. To further characterize the effect of different \ahfx values, we consider the largest absolute variation in the site energies depending on \ahfx by calculating the Chebyshev distance $D_{\ahfx} = \max\limits_{i}(|E_i(\ahfx=0.25) - E_i(\ahfx)|)$. From the results listed in Tab.~\ref{tab:maxEi}, one can see that on individual level the site energies can vary substantially, with more than \unit[0.1]{eV}. This variation is larger than the recorded values of $\sigma$ and with all \ahfx yielding the same mean site energy of \unit[-0.86]{eV} this could indicate non-neglibible effects on charge transport.

@@

\subsection{Electronic couplings}
